Figures for Paper

### 2021-07-19 paper_figures.Rmd
Update paper_figures.Rmd

@@

p2_shsy <- ggplot(df %>% filter(classification != "",
                                type=="SHSY5Y"), aes(x = name, y = 100*fraction, fill = class2,
                                                     colour = class2)) +
    geom_bar(stat="identity", position="dodge") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    ggtitle("SH-SY5Y") +
    xlab("") +
    ggeasy::easy_add_legend_title("") 
p2_shsy | p2_patient
```

>>>>

df[is.na(df)] <- 0

@@

p2_shsy <- ggplot(df %>% filter(classification != "",
                                type=="SHSY5Y"), aes(x = name, y = 100*fraction, fill = class2,
                                                     colour = class2)) +
    geom_bar(stat="identity", position="dodge") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    ggtitle("SH-SY5Y") +
    xlab("") +
    ggeasy::easy_add_legend_title("") 
p2_shsy | p2_patient

# fractional

df2 <- df %>%
    filter(classification != "Neither") %>%
    group_by(name) %>%
    mutate(f = n/sum(n))

ggplot(df2, aes(x = name, y = 100*f, fill = classification)) +
    geom_bar(stat="identity") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    xlab("") +
    ggeasy::easy_add_legend_title("")

ggsave("C:/Users/ogw/Google Drive/UCL PhD/Year 2/unc13a/nanopore/nanopore_100.svg",
       height = 10, width = 12, units = "cm")

ggplot(df2 %>%
           filter(type == "Patient"), aes(x = name, y = 100*f, fill = classification)) +
    geom_bar(stat="identity") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    xlab("") +
    ggeasy::easy_add_legend_title("") |
    ggplot(df2 %>%
           filter(type != "Patient"), aes(x = name, y = 100*f, fill = classification)) +
    geom_bar(stat="identity") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    xlab("") +
    ggeasy::easy_add_legend_title("")

ggsave("C:/Users/ogw/Google Drive/UCL PhD/Year 2/unc13a/nanopore/nanopore_100_separate.svg",
       height = 10, width = 12, units = "cm")
